Reproducible Research Peer Assessment 1 
========================================================

#### Loading and preprocessing the data

Load the data from the folder "repdata_data_activity"

```{r}
dat <- read.csv("./repdata_data_activity/activity.csv")
```



#### mean total number of steps taken per day

1.Histogram of the total number of steps taken each day

```{r}
ttlSteps <- aggregate(dat$steps, by=list(Category=dat$date), FUN=sum)
```

```{r fig.width=7, fig.height=6}
barplot(ttlSteps$x)
```


2.Calculate and report the mean and median total number of steps taken per day

```{r}
mean <- mean(ttlSteps$x, na.rm=T)
median <- median(ttlSteps$x, na.rm=T)
```

The mean total number of steps taken per day is `r mean`.  
The median total number of steps taken per day is `r median`.  


#### the average daily activity pattern
1.Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)  

```{r}
aveSteps <- aggregate(dat$steps, by=list(int=dat$interval), FUN=mean, na.rm=T)
```


```{r fig.width=7, fig.height=6}
plot(aveSteps$int,aveSteps$x, type="l")
```


2.Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
max <- aveSteps[aveSteps$x == max(aveSteps$x),]$int
```

`r max` contains the maximum number of steps.