Reproducible Research Peer Assessment 1 
========================================================

  
    
## Loading and preprocessing the data

Load the data from the folder "activity"

```{r}
dat <- read.csv("./activity/activity.csv")
```

  

## mean total number of steps taken per day

#### 1.Histogram of the total number of steps taken each day

```{r}
total <- aggregate(steps~date,data=dat,sum,na.rm=TRUE)

hist(total$steps)
```


#### 2.Calculate and report the mean and median total number of steps taken per day

```{r}
meansteps <- mean(total$steps, na.rm=T)
mediansteps <- median(total$steps, na.rm=T)
```

The **mean** total number of steps taken per day is `r meansteps`.  
The **median** total number of steps taken per day is `r mediansteps`.  
  


## the average daily activity pattern
#### 1.Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)  

```{r}
average <- aggregate(steps~interval,data=dat, mean, na.rm=T)  
plot(steps~interval,data=average,type="l")
```



#### 2.Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
maxsteps <- average[average$steps == max(average$steps),]$interval
```

Interval **`r maxsteps`** contains the maximum number of steps.  

## Imputing missing values
#### 1.Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r}
totalNA <- sum(is.na(dat$steps))
```

The total number of missing values in the dataset is **`r totalNA`**.

#### 2.Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated.
I use the mean of that interval to replace NA.


#### 3.Create a new dataset that is equal to the original dataset but with the missing data filled in.

```{r}
## copy the original data frame to newData
newData <- dat
## find index of NA values in steps
indx <- which(is.na(newData$steps)==TRUE) 
## replace NA with mean for that interval
for( i in indx) {
        newData[i ,"steps"] <- average[which(average$interval == dat[i, ]$interval),]$steps
}

```

#### 4.Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. Do these values differ from the estimates from the first part of the assignment? What is the impact of imputing missing data on the estimates of the total daily number of steps?

```{r}
totalNew <- aggregate(steps~date,data=newData,sum,na.rm=TRUE)

hist(totalNew$steps)

meanstepsNew <- mean(totalNew$steps, na.rm=T)
medianstepsNew <- median(totalNew$steps, na.rm=T)
```

The **mean** total number of steps taken per day is `r meanstepsNew`.  
The **median** total number of steps taken per day is `r medianstepsNew`.  

The **mean** value is the **same** as the value before imputing missing data because we put the mean value for that particular 5-min interval. The median value shows **a little** increase : but it depends on **where the missing values were**.


## Are there differences in activity patterns between weekdays and weekends?

#### 1.Create a new factor variable in the dataset with two levels - "weekday" and "weekend" indicating whether a given date is a weekday or weekend day.

```{r echo=TRUE}
newData$day=ifelse(as.POSIXlt(as.Date(newData$date))$wday%%6==0,
                          "weekend","weekday")
# For Sunday and Saturday : weekend, Other days : weekday 
newData$day=factor(newData$day,levels=c("weekday","weekend"))
```

#### 2.Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). The plot should look something like the following, which was creating using simulated data:

```{r echo=TRUE}
stepsInterval2=aggregate(steps~interval+day,newData,mean)
library(lattice)
xyplot(steps~interval|factor(day),data=stepsInterval2,aspect=1/2,type="l")

```

According to the plot above, there are difference in activity patterns between weekdays and weekends.